Sentence Generation as Planning with Probabilistic LTAG\\

### 2010-05-21 trunk/Papers/pcrisp-10/experiments.tex

\subsection{Results}
Table \ref{results} presents our results. In each experiment we count how many sentences in the test set produce an output at all (column `generated') and for how many the planner requires more than 5 minutes (column `timeout'. The search is terminated in this case). Some sentences cannot be realized at all (column `fail'), due to data sparseness problems. In such cases either no elementary tree with the required lexical content was seen in the training data, or the model assigns a zero probability to a required adjunction or substitution operation. We compute the average generation tree accuracy (column `acc') over all generated sentences.

>>>>

\subsection{Results}
Table \ref{results} presents our results. In each experiment we count how many sentences in the test set produce an output at all (column `success') and for how many the planner requires more than 5 minutes (column `timeout'. The search is terminated in this case). Some sentences cannot be realized at all (column `fail'), due to data sparseness problems. In such cases either no elementary tree with the required lexical content was seen in the training data, or the model assigns a zero probability to a required adjunction or substitution operation. We compute the average generation tree accuracy (column `acc') over all generated sentences.

### 2010-05-21 trunk/Papers/pcrisp-10/related.tex

Our treatment of integrated sentence planning and surface realization as planning, is inherited directly from {\sc crisp} \cite{kollerstone2007}.  Planning has long played a role in generation, but has focused on discourse planning instead of specifically addressing sentence generation \cite{hovy1988,appelt1992}. The applicability of these ideas was limited at that time because efficient planning technology was not available. Recently the development of more efficient planning algorithms (e.g. \newcite{hoffmannnebel2001,richterwestphal2008}) spawned a renewed interest in planning for NLG.  
{\sc Crisp} uses such efficient algorithms to efficiently solve the sentence generation problem defined by {\sc spud} \cite{stonedoran1997}. {\sc Spud}, which instead used an incomplete greedy algorithm, is based on an {\sc ltag} whose trees are augmented with semantic and pragmatic constraints. Given a communicative goal, a solution to the {\sc spud} problem realizes this goal and simultaneously selects referring expressions. The next section explores this idea in more detail.

>>>>

Our treatment of integrated sentence planning and surface realization as planning, is inherited directly from {\sc crisp} \cite{kollerstone2007}.  Planning has long played a role in generation, but has focused on discourse planning instead of specifically addressing sentence generation \cite{hovy1988,appelt1992}. The applicability of these ideas was limited at that time because efficient planning technology was not available. Recently the development of more efficient planning algorithms \cite{hoffmannnebel2001,richterwestphal2008} spawned a renewed interest in planning for NLG.  
{\sc Crisp} uses such algorithms to efficiently solve the sentence generation problem defined by {\sc spud} \cite{stonedoran1997}. {\sc Spud}, which instead used an incomplete greedy algorithm, is based on an {\sc ltag} whose trees are augmented with semantic and pragmatic constraints. Given a communicative goal, a solution to the {\sc spud} problem realizes this goal and simultaneously selects referring expressions. The next section explores {\sc crisp} in more detail.
